% Chapter Template

\chapter{Reflection of the project work} % Main chapter title

The synchronizing between the team members was always good, we had no problems talking to each other, except some typical technical problems that occur when working in a remote team.
It was good that each team member had his area of knowledge, and we managed to combine our different knowledges in more domains in order to make this course successful.

\section{What are your learning points, the most important things that you learnt from this virtual team work?}
\begin{itemize}
\item Synchronization with other team members
\item Patience
\item Punctuality
\item Delimitation of each members tasks, in order not to come to the point where 2 people are working at the same thing at the same time
\end{itemize}

\section{What advice would you give teams collaborating in software development? Come up with five "Golden Rules" and explain them}

\begin{itemize}
	\item  Always be on time at meetings
	It is important and polite to always be on time at meetings.
	\item  Always come prepared to meetings
	In order that a meeting to be successful and to fulfill its scope, it is important that every team member should come prepared with questions, and if he has something to present he should prepare his presentation accordingly. 
	\item  Synchronize constant with team members
	In order to avoid double or useless work it is important always to synchronize with team members. Never start to implement or to do task that were not discussed with others.
	\item Always try to finish tasks in time
	For a successfully delivery it is important to finish tasks in time. If possible, of course, because sometimes the estimations are different than the reality, but always try your best.
	\item Always discuss decisions 
	Never start to implement or to do some task before discussing with the team. This violates the concept of a team and the work that you maybe intend to do is maybe useless or wrong.
\end{itemize}