% Chapter Template

\chapter{Introduction} % Main chapter title

\label{Introduction} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\section{Introduction}
In this paper I will present the steps and technologies used for an IOT project in the healthcare field.

\section{Motivation}
From my point of view, software development is a means of helping people in various fields and making their lives easier with technology.
In 5 years of studying  and 4 years working as a Software Developer in different
companies and fields I learned how to create software for different proposes, like marketing,
sales and automotive.

I strongly believe that being a software developer gives you endless possibilities to help yourself and those around you. The medical field offers some of the most exciting possibilities to develop innovative technology that can make an actual difference in people's lives. Obviously, a Software Developer cannot replace an actual doctor, but they can develop tools to aid the said doctor in saving lives. With this idea in mind, I decided that the best use of my knowledge is in the medical field and I wanted to develop an application that would be useful to the population.
Thus, IOT Healthcare is an application that can be used in hospitals and other medical facilities, like asylums, hospices or nursing homes to better analyze the condition of the patients. I am convinced that if my project will eventually be implemented in these facilities, it will be a great help for the caretakers and patients alike.



\section{Target}

IOT Healthcare provides an analysis platform for specialists, where they can monitor the patient's symptoms. The system allows the concatenation of different sensors to a back-end application that can run analysis on the provided data. For now, the application can be connected to a smart band that can register activities like number of steps, heart beat, sleep duration. All this data is saved in the database and can be accessed from the web interface. With this information made available to us, we can extract statistics like the correlation between age and heart rate, if a certain medicine makes you sleep more or monitoring the patient's physical activity according to the evolution of their affection, etc.