% Chapter Template

\chapter{Chapter Title Here} % Main chapter title

\label{Chapter3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Chapter 3. \emph{Chapter Title Here}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Automotive industry}

The term automotive was created from Greek autos (self), and Latin motivus (of motion) to represent any form of self-powered vehicle.

It represents all those companies and activities involved in the manufacture of motor vehicles, including most components, such as engines and bodies. It is one of the world's most important economic sectors by revenue. The automotive industry does not include industries dedicated to the maintenance of automobiles following delivery to the end-user, such as automobile repair shops and motor fuel filling stations.

By allowing consumers to commute long distances for work, shopping, and entertainment, the auto industry has encouraged the development of an extensive road system, made possible the growth of suburbs and shopping centers around major cities, and played a key role in the growth of ancillary industries, such as the oil and travel businesses. The auto industry has become one of the largest purchasers of many key industrial products, such as steel. The large number of people the industry employs has made it a key determinant of economic growth.




\section{Infotainment}

Infotainment systems combine entertainment, multi-media and driver information functions in one module. In-Vehicle Infotainment (IVI) systems frequently utilize Bluetooth technology and/or smartphones to help drivers control the system with voice commands, touchscreen input, or physical controls.
Infotainment software has become a very influential component in today’s automotive market and more consumers are influenced by a car’s technology when making the decision to buy a car. Cars providing navigation systems, entertainment, and great user interfaces catch a higher percentage of the market. 
While each IVI system is different, typical tasks that can be performed with such a system include managing and playing audio content, utilizing navigation for driving, delivering rear-seat entertainment such as movies, games, social networking, etc., listening to incoming and sending outgoing SMS text messages, making phone calls, and accessing Internet-enabled or smartphone-enabled content such as traffic conditions, sports scores and weather forecasts.
